### 2017-02-01 doc/manuscript.Rmd
Moved detailed PLS results to Supplemental Material

To determine which components to use, internal CV showed that the first two
components gave the highest amount of explained variance (data not shown).
Confirming the findings from the GEE models, PLS analysis on the beta-cell
function measures revealed that there was a low correlation (though significant
at p`r cor_pls_igi$p`) between the predicted values and the actual values (r=
`r cor_pls_igi$r` to `r cor_pls_issi2$r`), suggesting poor predictability. While 
the clustering of TAGFA from the PLS results of the beta-cell function measures 
were similar to the insulin sensitivity measures, only the insulin sensitivity 
measures are presented given the higher predictive ability.

The PLS results for the insulin sensitivity (`r cite_f('pls')`) revealed a clustering 
of the fatty acids 14:0, 14:1n-7, 16:0, and 16:1n-7. These TAGFA loaded strongly (meaning
the fatty acids fell between the dashed and solid circles) and negatively on HOMA2-%S
and ISI, suggesting this cluster of TAGFA tracks together with lower insulin
sensitivity. The TAGFA 20:2n-6, 20:5n-3, 22:5n-3, and 22:6n-3 loaded positively
on both insulin sensitivity measures. No other TAGFA loaded strongly, the
results of which remained after running the PLS model on the cross-validated
testing set. The PLS model for insulin sensitivity had good predictive ability, 
determined by correlating the predicted outcome values with the actual values
(HOMA2-%S: `r cor_pls_homa2$r_p`; ISI: `r cor_pls_isi$r_p`).

@@

Generalized estimating equations (GEE) is a technique similar to mixed effects
modeling, except it calculates the marginal population averages compared to the
individual averages in mixed effects models. GEE is well suited and commonly
used in longitudinal cohort studies, especially given it's capacity to handle
missed visits.

@@

>>>>

Confirming the findings from the GEE models, PLS analysis on the beta-cell
function measures revealed that there was a low correlation (though significant
at p`r cor_pls_igi$p`) between the predicted values and the actual values (r=
`r cor_pls_igi$r` to `r cor_pls_issi2$r`), suggesting poor predictability. While 
the clustering of TAGFA from the PLS results of the beta-cell function measures 
were similar to the insulin sensitivity measures, only the insulin sensitivity 
measures are presented given the higher predictive ability.

The PLS results for the insulin sensitivity (`r cite_f('pls')`) revealed a clustering 
of the fatty acids 14:0, 14:1n-7, 16:0, and 16:1n-7. These TAGFA loaded strongly (meaning
the fatty acids fell between the dashed and solid circles) and negatively on HOMA2-%S
and ISI, suggesting this cluster of TAGFA tracks together with lower insulin
sensitivity. The TAGFA 20:2n-6, 20:5n-3, 22:5n-3, and 22:6n-3 loaded positively
on both insulin sensitivity measures. No other TAGFA loaded strongly. The PLS
model for insulin sensitivity had good predictive ability, determined by
correlating the predicted outcome values with the actual values (HOMA2-%S: `r
cor_pls_homa2$r_p`; ISI: `r cor_pls_isi$r_p`).

@@

Generalized estimating equations (GEE) is a technique similar to mixed effects
modeling, except it calculates the marginal population estimates compared to the
subject-specific estimates in mixed effects models. GEE is well suited and commonly
used in longitudinal cohort studies, especially given it's capacity to handle
missed visits.

@@

We used internal 10-fold cross-validation to determine which components to
extract from the PLS analysis. Based on the internal cross-validation, the first
two components gave the highest amount of explained variance (data not shown),
of which we decided to use these two components in the final results.

The predictive capability of the PLS models were tested using cross-validation. 
The data set was randomly split in half into a training set and a testing set. 
After specifying the model on the training set, results were compared using the 
testing set to determine whether how predictive the model was given a new
dataset. Final results shown in the figures use the full dataset (rather than a
training or testing set)
